Pleiotropy of expression quantitative trait loci increases with the number of regulated genes, active cell types and tissues and bound transcription factors

### 2023-02-06 ms/ms06_floats.tex
ENH updated supplementary
ENH

@@

% full size table is table
\begin{table}[!tbp]
    \centering
    \scriptsize
%\hline
    \csvreader[separator=tab,
    tabular=crclcp{0.4\textwidth},
    head,
    table head=\bfseries Chrom. & \bfseries Pos (hg38) & \bfseries Cytoband & \bfseries RSID & \bfseries Gene marker& \bfseries GWAS Categories\\\hline,
    ]{\floatRelativePath/cmpt_count_per_rsid.py/count_per_rsid_gwas_ms.tsv}{}% use head of csv as column names
        {\csvcoli\ & \csvcolii\ & \csvcoliii\ & \csvcoliv\ & \csvcolv\ & \csvcolvi}% specify your coloumns here
%\hline
%
    \vspace{15pt}
%
    \caption{Example eQTLs involved in four GWAS categories in different cytobands.
    The gene marker is the eQTL gene with the highest PubMed publication count.
    The whole list is given in the Supplementary files.}
    \label{tab:pleitropic_variants}
\end{table}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%% Fig 1: Comorbidity matrix
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\begin{figure}[!tbp]
    \centering
%
    \includegraphics[width=\textwidth]{\floatRelativePath/plthst_perc_tophits_eqtl.py/hist_perc_tophits_eqtl_excl_mhc.png}
%
    \caption{Histogram showing the percentage of GWAS with the percentage of their tophits colocalized with eQTLs.
    I have excluded tophits in in the MHC locus in chromosome 6 between 25,000,000 and 35,000,000,
    because this locus is not included in the colocalization pipeline.}
    \label{fig:hist_perc_tophits_eqtl_excl_mhc}
%
\end{figure}

@@

% full size table is table
\begin{table}[!tbp]
    \centering
    \scriptsize
%\hline
    \csvreader[separator=tab,
    tabular=crclcp{0.4\textwidth},
    head,
    table head=\bfseries Chrom. & \bfseries Pos (hg38) & \bfseries Cytoband & \bfseries RSID & \bfseries Gene marker& \bfseries GWAS Categories\\\hline,
    ]{\floatRelativePath/cmpt_count_per_rsid.py/count_per_rsid_gwas_ms.tsv}{}% use head of csv as column names
        {\csvcoli\ & \csvcolii\ & \csvcoliii\ & \csvcoliv\ & \csvcolv\ & \csvcolvi}% specify your coloumns here
%\hline
%
    \vspace{15pt}
%
    \caption{Example eQTLs involved in four GWAS categories in different cytobands.
    The gene marker is the eQTL gene with the highest PubMed publication count.
    The whole list is given in the Supplementary table ST2.}
    \label{tab:pleitropic_variants}
\end{table}
